---
title: "Data Analysis for The Office"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    vertical_layout: fill
    logo: img/logo.JPG
---
<style>                     
.metricsgraphics-legend {
  margin-top:-20px;
  font-size:10pt;
  text-align:center;
}

.navbar {
  background-color:black;
  border-color:white;
  font-family: 'Courier New', monospace;
  font-weight: bold;
}

.navbar-brand {
color:white!important;
}

.sidebar { font-size: 13px; }
</style> 

```{r setup, include=FALSE}
library(flexdashboard)
library(metricsgraphics)
library(flexdashboard)
library(schrute)
library(plotly) 
library(rtweet)
library(stringr)
library(tidytext)
library(dplyr)
library(ggplot2)
library(maps)
library(raster)
library(rgdal)
library(classInt)
library(RColorBrewer)
library(crosstalk)
library(tidyr)
library(wordcloud2)
library(wordcloud)
library(stringr)
library(varhandle)
library(igraph)
library(networkD3)
```
Column {.sidebar data-width=190}
-----------------------------------------------------------------------
**About**: 

This dashboard includes visualization and analysis of the **most popular TV show in 2018 (as shown in the map), the Office. **

Users can hover on the **time series plot** to find the best episodes in each season. Season 3 has the **highest** and season 8 has the **lowest** average ratings. 

Users can also check the **word clouds** for 4 main characters (Michael, Dwight, Jim and Pam, aka “MDJP”)  and 2 other characters, Andy and Creed, as they are my personal favorites (LOL). 

Don’t forget to check out other tabs, the **network** of character relationships (with MDJP and their top 10 friends in the office), and a **lollipop plot** which shows the number of mentions for MDJP from 2000 random ‘the office-related’ posts on twitter.

**Author**: Beixuan Jia (bj256)

**Software**: R

**Data source**: 

* [fave TV shows by each state](https://www.insider.com/most-binged-tv-show-by-state-2018-8#arkansas-roseanne-4)
* [script](https://docs.google.com/spreadsheets/d/18wS5AAwOh8QO95RwHLS95POmSNKA2jjzdt0phrxeAE0/edit#gid=747974534)
* [IMDb Rating for each Episode](https://www.kaggle.com/kapastor/the-office-imdb-ratings-per-episode)


Column {data-width=500}
-----------------------------------------------------------------------
### Map: Most-binged TV show in every state in 2018
```{r}
## Read in data
us_states <- map_data("state")
show <- read.csv("data/show.csv")
show_freq <- data.frame(table(show$pop_show))
## Change variable names
names(show_freq)[names(show_freq)=='Var1'] <- 'Show'
## Find the most popular show in 2018
show_freq = show_freq %>% mutate(rank = dense_rank(desc(Freq)))
show_freq = show_freq[(order(show_freq$rank)),]

## Prepare the dataset for map
## Join show and the freqency table
show <- left_join(show, show_freq, by=c('pop_show'='Show'))
## Find the most popular show
show = show[(order(show$rank)),]
## Change variable name
names(show)[names(show)=='ï..state'] <- 'state'
## Covert the state names to lower cases
show$region <- tolower(show$state)

## Join show data and map data
show_map <- left_join(show, us_states, by=c('region'='region'))
# show_map$subregion <- NULL
show_map$state <- NULL
## reorder legend
show_map$label <- factor(show_map$label, levels = c("The Office", "13 Reasons Why", "Grey's Anatomy", "Supernatural", "Friends", "other"))
```

```{r, fig.height=8, fig.width=12}
## custom colors for the map
mycolors = c(brewer.pal(name="Set3", n = 4), brewer.pal(name="Set1", n = 2))

## create grid
p0 <- ggplot(data = show_map,
            aes(x = long, y = lat, group = group, fill = label)) + theme_bw()

p1 = p0 + geom_polygon(color = "#453d35", size = 0.1) +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45)

## create map
p2 <- p1 +
  labs(title = "The most-binged TV show in every state in 2018", fill = NULL) + scale_fill_manual(values=c("#377EB8", "#8DD3C7", "#BEBADA", "#e78b8b", "#f0b873", "#f9f9d8")) + theme(plot.title = element_text(hjust = 0.5), text = element_text(size = 20))

p2
```


### Time Series: IMDb Rating of Each Episode
```{r}
## Read in data
rate <- read.csv("data/rating.csv")
rate <- rate[, -which(names(rate) %in% c('Description','Num_Votes'))]

## Re-create episode variable
eps <- c(1:26)
eps <- as.factor(eps)
```

```{r}
## Filter the rating variable by seasons
rate1 <- subset(rate, Season == 1)$Rating
rate2 <- subset(rate, Season == 2)$Rating
rate3 <- subset(rate, Season == 3)$Rating
rate4 <- subset(rate, Season == 4)$Rating
rate5 <- subset(rate, Season == 5)$Rating
rate6 <- subset(rate, Season == 6)$Rating
rate7 <- subset(rate, Season == 7)$Rating
rate8 <- subset(rate, Season == 8)$Rating
rate9 <- subset(rate, Season == 9)$Rating
```

```{r}
## Create a new dataframe with episode numbers and seasons
lines <- data.frame(eps, rate1, rate2, rate3, rate4, rate5, rate6, rate7, rate8, rate9)
```

```{r}
## Create the time series plot: add rating data from 9 seasons

fig <- plot_ly(lines, x = ~eps, y = ~rate1, name = 'Season 1', type = 'scatter', mode = 'lines', width = 1.5, hoverinfo = "Season", line = list(color = 'rgba(192,192,192,0.4)')) 
fig <- fig %>% add_trace(y = ~rate2, name = 'Season 2', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% add_trace(y = ~rate3, name = 'Season 3', line = list(color = 'rgb(205, 12, 24)'))
fig <- fig %>% add_trace(y = ~rate4, name = 'Season 4', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% add_trace(y = ~rate5, name = 'Season 5', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% add_trace(y = ~rate6, name = 'Season 6', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% add_trace(y = ~rate7, name = 'Season 7', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% add_trace(y = ~rate8, name = 'Season 8', line = list(color = 'rgb(22, 96, 167)'))
fig <- fig %>% add_trace(y = ~rate9, name = 'Season 9', line = list(color = 'rgba(192,192,192,0.4)'))
fig <- fig %>% layout(title = "IMDb Rating of Each Episode",
         xaxis = list(title = "Episode"),
         yaxis = list (title = "IMDb Rating"))

fig
```

Column {.tabset data-width=350}
-----------------------------------------------------------------------
### Wordcloud

```{r}
## Read in data
df <- schrute::theoffice
## Create a dataset with characters and their scripts only
script <- df[,c('character','text')]
```

```{r}
## Token Script
token.script <- script %>% 
# dplyr::filter(character == "Pam") %>% 
tidytext::unnest_tokens(word, text)

## Define stop words and remove them from the script
stop_words <- tidytext::stop_words
tidy.token.script <- token.script %>% dplyr::anti_join(stop_words, by = "word")

## Count frequency for each unique word from the script
word_freq = tidy.token.script %>% 
  group_by(character) %>% 
  dplyr::count(word, sort = TRUE) 
word_freq = data.frame(word_freq)

## Add more stepwords and remove them from the word frequency table
word_list = c("uh", "ah", "um", "huh", "yeah", "hey", "gonna")
word_freq <- word_freq[! word_freq$word %in% word_list, ]

## Rename variable
names(word_freq)[names(word_freq)=='n'] <- 'freq'

## Define the main characters. Only keep words that the main characters used
main_char = c("Michael", "Dwight", "Jim", "Pam", "Andy", "Angela", "Kevin", "Erin", "Oscar", "Creed")
word_freq <- word_freq[word_freq$character %in% main_char, ]
```

```{r}
## Create subplots 
par(mfrow=c(2,3))

## Function: return a wordcloud for each main character
top_wc <- function(x) {
  par(mar = rep(0,4))
  data = subset(word_freq, character == x)
  wordcloud(words = data$word, freq = data$freq, min.freq = 5,
          # scale=c(1,0.25),
          scale=c(2,0.5),          
          max.words=100, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"), main = "hi") 
  mtext(paste0("Word cloud for ", x), side = 3, cex = 0.8, line = -1)
}

top_wc("Michael")
top_wc("Dwight")
top_wc("Jim")
top_wc("Pam")
top_wc("Andy")
top_wc("Creed")
```

### Network
```{r}
## Read in data, rename variables
library(stringr)
nw <- read.csv("data/network.csv")
names(nw)[names(nw)=='ï..source'] <- 'source'
nw$target = str_to_title(nw$target)

## Define Edges
edge = nw
library(varhandle)
edge$source <- unfactor(edge$source)

## Define Nodes
node1 <- unique(edge$target)
node2 <- unique(edge$source)
node <- c(node1, node2)
node <- unique(node)
node = as.data.frame(node) 

## Create groups: 1 - main characters; 2 - others
names(node)[names(node)=='node'] <- 'name'
node$group <- ifelse(node$name == 'Dwight' | node$name == 'Michael' | node$name == 'Jim' | node$name == 'Pam', 1, 2)
```

```{r}
library(igraph)
library(networkD3)

## Read in cleaned data for note and edges
MisLinks = read.csv("data/nw2.csv")
MisNodes = read.csv("data/node.csv")

## Change datatype 
MisNodes$group <- as.integer(MisNodes$group)
## Rename variable
names(MisLinks)[names(MisLinks)=='ï..source'] <- 'source'
## Adjust edge width
MisLinks$value_adj = MisLinks$value/25
```

```{r}
## Custom colors for the network nodes
ColourScale <- 'd3.scaleOrdinal()
            .domain(["main", "other"])
           .range(["#8961ab", "#a3e6f4"]);'

## Create network
fn <- forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value_adj", NodeID = "name",
             Group = "group", opacity = 0.9, Nodesize = 3, 
             linkDistance = 100, fontSize = 20,
             colourScale = JS(ColourScale))

## Add title
fn <- htmlwidgets::prependContent(fn, htmltools::tags$h3("Network for selected characters from the Office"))

## Adjust title format and background color
fn <- htmlwidgets::onRender(
  fn,
  'function(el, x) { 
    d3.selectAll(".legend text").style("fill", "white");
    d3.select("body").style("background-color", "#fffeee");
    d3.select("h3").style("justify-content", "center").style("text-align", "center");
  }'
)

fn
```

### Popularity on Tweeter 
```{r}
## Read in random 2000 tweets with #TheOffice
num_tweets <- 2000
TheOffice <- search_tweets('#TheOffice', n = num_tweets, include_rts = FALSE)

## Tokenize tweets and remove stop words
reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"
TheOffice_words <- TheOffice %>% dplyr::select (status_id, text) %>%
  filter(!str_detect(text, '^"')) %>%
  mutate(text = str_replace_all(text, "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
  unnest_tokens(word, text, token = "regex", pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

## Find the top 30 words
# TheOffice_words %>% group_by(word) %>% summarize(n = n()) %>% arrange(desc(n)) %>% top_n(30)

## Find the 5 most commonly used words for main characters
# TheOffice_Characters <- TheOffice_words %>% filter(word =='#michaelscott'| word=='michael' | word=='dwight' | word== 'jim' | word== 'pam')
# TheOffice_Characters %>% group_by(word) %>% summarize(n = n()) %>% arrange(desc(n)) %>% top_n(5)
```

```{r}
## Create a data with times of mentioning in tweets for each main character
Characters_Count <- data.frame("Name"=c("Michael", "Dwight", "Jim", "Pam"), "Mentions"= c(202,84,78,60), stringsAsFactors = FALSE)
```

```{r}
library(ggplot2)

## Create lolipop plot to show the number of mentioning on tweets by each main character
ggplot(Characters_Count, aes(x=Name, y=Mentions), label = Mentions) +
  geom_segment( aes(x=Name, xend=Name, y=0, yend=Mentions), color="skyblue") +
  geom_point( color="blue", size=7, alpha=0.6) +
  geom_text(label = Characters_Count$Mentions, color = "white", size = 3.5) +
  ggtitle("Popularity of characters from \n2000 random 'the Office-related' tweets") + xlab("Character Names") + ylab("Number of Mentions") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    plot.title = element_text(hjust = 0.5)
  )
```