---
title: "A7 - Networks"
author: "Beixuan Jia"
date: "11/7/2020"
output: html_document
fig_width: 20 
fig_height: 16 
---

```{r}
knitr::opts_chunk$set(fig.width=20, fig.height=16) 
library(dplyr)
library(ggplot2)
library(scales)
options(scipen = 999)
```

```{r}
library(readxl)
state <- read_excel("State_to_State_Migrations_Table_2018.xls")
```
##### Data Cleaning
Selected origin states: NY, TX, CA, MD 
```{r}
state <- state[,c(1, 19, 54, 81, 105)]
state <- state[-c(1:5),]
names(state) <- as.matrix(state[1, ])
state <- state[-1, ]
state[] <- lapply(state, function(x) type.convert(as.character(x)))
state <- state[-c(1:4),]
state = state[complete.cases(state), ]
names(state) <- c("curr_states", "California", "Maryland", "New York", "Texas") 
```

```{r}
state$California = as.numeric(as.character(state$California))
state$`New York` = as.numeric(as.character(state$`New York`))
state$Texas = as.numeric(as.character(state$Texas))
state$Maryland = as.numeric(as.character(state$Maryland))
```

##### Generate the top 10 destinations for the 4 states
```{r}
top_dest <- function(x) {
  rank <- state[order(-state[x]), ]
  rank <- rank[,c('curr_states', x)]
  rank$source <- x
  names(rank)[names(rank)=='curr_states'] <- 'target'
  names(rank)[names(rank)==x] <- 'count'
  rank = rank[,c(3,1,2)]
  head(rank, 10)
}

top_dest_NY <- top_dest("New York")
top_dest_TX <- top_dest("Texas")
top_dest_CA <- top_dest("California")
top_dest_MD <- top_dest("Maryland")
```

##### Define Edges
```{r}
edge <- do.call("rbind", list(top_dest_NY, top_dest_TX, top_dest_CA, top_dest_MD))
print(edge)
```

```{r}
library("varhandle")
edge$target <- unfactor(edge$target)
```

##### Define Nodes
```{r}
node1 <- unique(edge$target)
node2 <- unique(edge$source)
node <- c(node1, node2)
node <- unique(node)
```

```{r}
node = as.data.frame(node) 
```

##### Define Graph
```{r}
library(igraph)
```

Graph Info
```{r}
routes_igraph <- graph_from_data_frame(d = edge, vertices = unique(node), directed = TRUE)
routes_igraph
```

##### Plot the Graph
```{r}
# deg <- degree(routes_igraph, mode="all")
l <- layout_in_circle(routes_igraph)

plot(routes_igraph, 
     layout=l, 
     edge.arrow.size=2, 
     edge.color=rgb(0.1,0.7,0.8,0.5),
     vertex.label.size=7,
     vertex.label.cex=1.2, 
     vertex.label.font=10,
     vertex.shape="circle", 
     vertex.color="pink",
     vertex.size=23, 
     vertex.label.color="black", 
     edge.width=(edge$count)/4000)
```
The network graph shows that some popular destinations of people from the 4 states (NY, TX, CA and MD) are FL, CA, TX, NC, and VA. 

Other findings: 

* Among all 4 states, people from CA migrated the most and people from MD moved the least in 2018.
* The Top 5 destinations for CA residents are TX, AZ, WA, NV, and OR
* The Top 5 destinations for TX residents are CA, OK, CO, FL, and LA
* The Top 5 destinations for NY residents are NJ, FL, PA, CA, and CT
* The Top 5 destinations for MD residents are VA, PA, FL, TX, and DC

This tells us people would generally moved to their adjacent states, with exceptions of big traveling states or states with a lot of job opportunities, such as FL, TX and CA. It's also very interesting that CA and TX are each other's top 1 destination.
